---
title: "**A Simple Regression**"
subtitle: "**REPORT**"
author: "Roberto J. Alcaraz Molina"
date: "7/3/2021"
output: html_document
params:
  target: "Mileage"
  pred: "Price"
---

In this last panel we can see the relationship between the variables `Price`, `Age` and `Mileage` by selecting the target variable and the predictor variable. Moreover, each point has a different color depending on the car type. Finally, we can see the Pearson's correlation coefficient between the two selected variables.

```{r, echo=F}
data("ThreeCars")
```

The Pearson's correlation coefficient ($R^2$) between the variables `r params$pred` and `r params$target` is `r round(cor(ThreeCars[,params$target], ThreeCars[,params$pred]),4)` and below we can see the plot:

```{r, echo=F, warning=F, message=FALSE}
form <- as.formula(paste(params$target, " ~ ", params$pred))
fit <- lm(form, data = ThreeCars)

ggplot(data = ThreeCars, aes_string(x = params$pred, y = params$target)) +
  geom_point(aes(colour = CarType)) + 
  geom_smooth(method = "lm") +
  theme_bw()
```














